correlationstuff

### 2024-02-01 corstuff.Rmd
new lms with Kahan EFA scale

## Mean Perceived Risk and Mean Perceived Benefit for all energy technologies.

@@

##  Kahan scale Alpha values 
Hierarchy - Egalitarianism scale alpha  =  0.7
Individualism - Communitarianism scale alpha= 0.52
Only Individualism scale alpha = 0.31 
Only Communitarianism scale alpha = 0.72

@@

\blandscape
# Kahan scale EFA  
```{r, echo=FALSE}

#print.psych(kahan.fa, cut = 0.4, sort = TRUE)

## alternative Kahan scores
```{r, echo=FALSE}

@@

>>>>

@@

##  Kahan scale Alpha values 
Hierarchy - Egalitarianism scale alpha  =  0.70
Individualism - Communitarianism scale alpha= 0.52
Only Individualism scale alpha = 0.31 
Only Communitarianism scale alpha = 0.72

@@

## Alternative Kahan Scores with Mean across
```{r, echo=FALSE}

@@

\blandscape

# Kahan scale EFA  
```{r, echo=FALSE}

Kahan_scale1 <- codedmodule2 %>%
  dplyr::select(starts_with(c("Risky_Nuclear","K_", "Uppercaste", "Male", "Hindu", "Urban", "State","age"))) %>%
  mutate_at(vars(age), funs(case_when(. == "18-24 years old" ~ 1, 
                                      . == "25-34 years old" ~ 2,
                                      . ==  "35-44 years old" ~3,
                                      . == "45-54 years old" ~ 4,
                                      . == "55-64 years old" ~ 5,
                                      . == "65-74 years old" ~ 6,
                                      . == "75 years or older" ~ 7))) %>%
  na.omit()

Kahan_scale<- Kahan_scale1 %>%
  dplyr::select(starts_with("K_"))

print.psych(kahan.fa, cut = 0.4, sort = TRUE)

Kahanefa <- psych::factor.scores(Kahan_scale, kahan.fa)

# The factor scores will be stored in the scores element of the returned list
kahanefascores <- Kahanefa$scores

fascale_scores4 <- cbind(Kahan_scale1, kahanefascores) %>%
  rename(CE = MR1)%>%
  rename(HE = MR2) #%>%

# LMs with EFA Kahan factors

demoEFA <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + Urban, data = fascale_scores4)

summary(demoEFA)

# 2) lm with all demographic variables
demoEFA2<- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + Urban + age + State, data = fascale_scores4)
summary(demoEFA2)

# 3) lm with kahan 
demoEFA3 <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + Urban + age + State + CE + HE , data = fascale_scores4)

summary(demoEFA3)

#2.  Kahan scale EFA  
```{r, echo=FALSE}

Kahan_scale2<- fascales %>%
  dplyr::select(starts_with("K_"))

kahan2.fa <- fa(Kahan_scale2, nfactors = 2, rotate = "varimax")

print.psych(kahan2.fa, cut = 0.4, sort = TRUE)

Kahanefa2 <- psych::factor.scores(Kahan_scale2, kahan2.fa)

# The factor scores will be stored in the scores element of the returned list
kahanefascores2 <- Kahanefa2$scores

fascale_scores5 <- cbind(fascales, kahanefascores2) %>%
  rename(CE = MR1)%>%
  rename(HE = MR2) #%>%

# 2. LMs with EFA Kahan factors

KEFA <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + Urban, data = fascale_scores5)

summary(KEFA)

# 2) lm with all demographic variables
KEFA2<- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + Urban + age + State, data = fascale_scores5)
summary(KEFA2)

# 3) lm with kahan 
KEFA3 <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + Urban + age + State + CE + HE , data = fascale_scores5)

summary(KEFA3)
